Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-24 docs/PhysicsPaper/StokesErosion.tex
started on Sec 3

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%

@@

\nick{Perhaps we can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}

>>>>

%-----------------------------------------------------------------------------------------------%
\section{Boundary Integral Equation and Cauchy Integral Formulation}
\label{sec:DLP}
%-----------------------------------------------------------------------------------------------%
To accurately and efficently solve the Stokes
  equations~\eqref{eqn:StokesEq}, we reformulate the system as a
  boundary integral equation (BIE). We represent the velocity as the sum
  of a double-layer potential and a combination of Stokeslets and
  rotlets~\cite{pow-mir1987}
\begin{align}
  \uu(\xx) = \DDD[\eeta](\xx) = \frac{1}{\pi}\int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
    \eeta(\yy) \, ds_\yy, + \sum_{\ell=1}^{M}\left(S[\llambda_\ell](\xx) +
    R[\xi_\ell](\xx)\right), \quad \xx \in \Omega.
  \label{eqn:velocityDLP}
\end{align}
Note that $\bd\Omega$ includes both the eroding bodies and the outer
  boundary. The Stokeslet and the rotlets are
  \begin{align}
    S[\lambda_\ell](\xx) = \frac{1}{4\pi} \left(\log \rho_\ell +
    \frac{\rr_\ell \otimes \rr_\ell}{\rho_\ell^2} \right) \llambda_\ell,
    \quad
    R[\xi_\ell](\xx) = \frac{\rr_\ell^\perp}{\rho_\ell^2}\xi_\ell,
  \end{align}
  where $\rr_\ell = \xx - \cc_\ell$, $\rho_\ell = \|\rr_\ell\|$, and
  $\cc_\ell$ is a point inside body $\ell$.

@@
